
\begin{frame}[fragile]
\frametitle{NumPy module}

\begin{itemize}
\item Specific module for numerical simulations.
\item Very excellent for array manipulation.
\item Documentation from \url{https://www.numpy.org/}
\end{itemize}

%\newcommand{\newfilename}{py-matplotlib.py}
%\lstinputlisting[language=Python, firstline=1, lastline=7]{../py-matplotlib.py}
%file: \newfilename

\end{frame}

%-------------------------------------------------------------------------------

\begin{frame}[fragile]
\frametitle{SciPy module}

\begin{itemize}
\item Scientific calculations module.
\item Lots of functions for scientific computation.
\item Documentation from \url{https://www.scipy.org/}
\item Specific manuals \url{https://docs.scipy.org/doc/scipy-1.3.0/reference/}
\end{itemize}

%\newcommand{\newfilename}{py-matplotlib.py}
%\lstinputlisting[language=Python, firstline=1, lastline=7]{../py-matplotlib.py}
%file: \newfilename

\end{frame}

%--------------------------------------------------------------------------------

\begin{frame}[fragile]
\frametitle{Matplotlib module}

\begin{itemize}
\item Very efficient module for plotting almost everything.
\item Capable for plotting graphs and images.
\item Documentation from \url{https://matplotlib.org/3.1.0/index.html}
\end{itemize}

\newcommand{\newfilename}{py-matplotlib.py}
\lstinputlisting[language=Python, firstline=1, lastline=7]{../py-matplotlib.py}
file: \newfilename

\end{frame}

%-------------------------------------------------------------------------------

\begin{frame}[fragile]
\frametitle{pandas module}

\begin{itemize}
\item Python data analysis module.
\item The go-to module for data analysis.
\item Documentation from \url{https://pandas.pydata.org/}
\end{itemize}

%\newcommand{\newfilename}{py-matplotlib.py}
%\lstinputlisting[language=Python, firstline=1, lastline=7]{../py-matplotlib.py}
%file: \newfilename

\end{frame}

%-------------------------------------------------------------------------------

\begin{frame}[fragile]
\frametitle{Numba module}

\begin{itemize}
\item Python module for high performance computing.
\item Just-In-Time (JIT) compiler for faster computation.
\item Documentation from \url{https://numba.pydata.org/}
\end{itemize}

%\newcommand{\newfilename}{py-matplotlib.py}
%\lstinputlisting[language=Python, firstline=1, lastline=7]{../py-matplotlib.py}
%file: \newfilename

\end{frame}

%-------------------------------------------------------------------------------
